Differnces-in-Differences with Spatial Spillover

### 2020-12-03 latex/slides/Spillover_slides.tex
Added TVA section to slides and small edits

\documentclass[aspectratio=169]{beamer}
% Metropolis Theme ------------------------------------------------------------------------------
\usetheme{metropolis} % Use metropolis theme

@@

@@

\begin{frame}{Potential Outcomes Framework}
    For exposition, I will label units as counties. Assume all treatment occurs at the same time (2-periods or pre-post averages).\footnote{This form adapts the framework of Vazquez-Bare (2020) for the diff-in-diff setting.}

@@

\begin{frame}{Parallel Trends}
    \begin{itemize}
        \item I assume a modified version of the parallel trends assumption: \[
            \mathbb{E}\left[ Y_{i,1}(0, 0) - Y_{i,0}(0, 0) \mid D_i = 1, \vec{D} = 0 \right] 
        \] \[
            \quad =
            \mathbb{E}\left[ Y_{i,1}(0, 0) - Y_{i,0}(0, 0) \mid D_i = 0, \vec{D} = 0 \right],
        \]

        \item In the complete absence of treatment (not just the absence of individual $i$'s treatment), the change in potential outcomes from period 0 to 1 would not depend on treatment status
    \end{itemize}
\end{frame}

\begin{frame}{What does Diff-in-Diff identify?}
    \begin{itemize}
        \item With that, I decompose the diff-in-diff estimate as follows:

@@

\begin{frame}{Example of Bias Simulation}
    \textbf{Treated Spillover:}

@@

\begin{frame}{Tennessee Valley Authority}

\begin{frame}
\begin{table}[ht]
    \caption{Effects of Tennessee Valley Authority on Decadel Growth}
    \label{tab:tva}
    \renewcommand{\arraystretch}{1}

@@

                & \multicolumn{1}{c}{\textbf{Kline \& Moretti (2011)}} & \multicolumn{4}{c}{\textbf{Diff-in-Diff with Spillovers}} \\ 
                \cmidrule{2-2} \cmidrule{3-6} 
                & & & TVA between & TVA between & TVA between \\ 
                \textit{Dependent Var.} & TVA & TVA & 0-100 mi. & 100-250 mi. & 250-500 mi. \\

>>>>

\documentclass[aspectratio=43]{beamer}
% Metropolis Theme ------------------------------------------------------------------------------
\usetheme{metropolis} % Use metropolis theme

@@

\addbibresource{references.bib}

@@

\begin{frame}{Potential Outcomes Framework}
    For exposition, I will label units as counties. Assume all treatment occurs at the same time (2-periods or pre-post averages).\footnote{This form adapts the framework of \citet{Vazquez-Bare_2019} for the diff-in-diff setting.}

@@

\begin{frame}{Parallel Trends}
    I assume a modified version of the parallel trends assumption: 
    \[
        \mathbb{E}\left[ Y_{i,1}(0, 0) - Y_{i,0}(0, 0) \mid D_i = 1, \vec{D} = 0 \right] 
    \] \[
        \quad =
        \mathbb{E}\left[ Y_{i,1}(0, 0) - Y_{i,0}(0, 0) \mid D_i = 0, \vec{D} = 0 \right],
    \]

    \begin{itemize}
        \item In the complete absence of treatment (not just the absence of individual $i$'s treatment), the change in potential outcomes from period 0 to 1 would not depend on treatment status
    \end{itemize}
\end{frame}

\begin{frame}{What does Diff-in-Diff identify?}
    With the parallel trends assumption and random assignment of $D_i$, I decompose the diff-in-diff estimate as follows:

@@

\begin{frame}{Example of Bias}
    \textbf{Treated Spillover:}

@@

\begin{frame}{Tennessee Valley Authority}
    \citet{Kline_Moretti_2014} look at the long-run impacts of the Tennessee Valley Authority (TVA).

    \begin{itemize}
        \item The TVA was a large-scale federal investment started in 1934 that focused on improving manufacturing economy.

        \item The program focused on electrification through dams and transportation canals in order to improve the manufacturing economy

        \item Hundreds of dollars spent anually per person
    \end{itemize}
\end{frame}

\begin{frame}{Identification}
    \citet{Kline_Moretti_2014} run the county-level difference-in-differences  specification: 
    \begin{equation}\label{eq:tva_spillover}
        y_{c, 2000} - y_{c, 1940} = \alpha + \text{TVA}_c \tau + X_{c, 1940} \beta + (\varepsilon_{c, 2000} - \varepsilon_{c, 1940})
    \end{equation}

    \begin{itemize}
        \item $y$ are outcomes for agricultural employment, manufacturing employment, and median family income.
        \item $\text{TVA}_c$ is the treatment variable
        \item $X_{c, 1940}$ allow for different long-term trends based on covariates in 1940. 
    \end{itemize}

    They trim the sample using a logit regression to predict treatment using $X_{c,1940}$ and keep control units in the top 75\% of predicted probability.
\end{frame}

\begin{frame}{Spillovers in the TVA Context}
    In our context, there is reason to believe spillovers can occur to nearby counties

    \begin{itemize}
        \item Agricultural employees might be drawn to hire wages for new manufacturing jobs in Tennessee Valley

        \item Manufacturing jobs that would have been created in the control units in the absence of treatment might move to the Tennessee Valley

        \item Since manufacutring jobs pay higher than agricultural jobs, the above two spillover effects can cause changes in median family income
    \end{itemize}
\end{frame}

\begin{frame}{Specification including spillovers}
    \begin{equation}
        \Delta y_c = \alpha + \text{TVA}_i \tau + \sum_{d \in \text{Dist}} \text{Between}(d)\delta_d + X_{i, 1940} \beta + \Delta \varepsilon_c
    \end{equation}

    \begin{itemize}
        \item $\text{Between}(d)$ is a set of indicators for being in the following distance bins (in miles) from the Tennessee Valley Authority: 
        \[ d \in \left\{ (0, 50], (50, 100], (100, 150] \right\} \]
    \end{itemize}
\end{frame}

\imageframe{../../figures/figure-tva-sample_slides.pdf}

\begin{frame}
\begin{table}[ht]
    \caption{Effects of Tennessee Valley Authority on Decadel Growth}
    \label{tab:tva}
    \renewcommand{\arraystretch}{1.2}

@@

                & \multicolumn{1}{c}{\textbf{Diff-in-Diff}} & \multicolumn{4}{c}{\textbf{Diff-in-Diff with Spillovers}} \\ 
                \cmidrule{2-2} \cmidrule{3-6} 
                & & & TVA between & TVA between & TVA between \\ 
                \textit{Dependent Var.} & TVA & TVA & 0-50 mi. & 50-100 mi. & 100-150 mi. \\
